Notes on Perturbational Quantities

### 2008-08-14 docs/pert_notes/paper.tex
merge in the flow_chart.tex tables to help make sense of all of this mess
make the tables reflect what is actually in the code

\def\eb    {{\bf e}}
\def\Ub    {{\bf U}}
\def\Ubt   {\widetilde{\bf U}}
\def\wt    {\widetilde{w}}

@@

+ \nabla\cdot\kappa\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\

@@

+ \underbrace{\psi + \wt\frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kappa\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.

@@

+ \wt\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 

@@

+ \psi + \wt\frac{\partial p_0}{\partial r} + \nabla\cdot\kappa\nabla T. \label{rhoh equation}

@@

- \nabla\cdot[(\rho h)_0\Ubt] + \wt\frac{\partial p_0}{\partial r} 
+ \nabla\cdot\kappa\nabla T\nonumber \\

@@

- \nabla\cdot[(\rho h)_0\Ubt] + \wt\frac{\partial p_0}{\partial r}
+ \nabla\cdot\kappa\nabla T}_{"(\rho h)' ~ \text{force}"}. \label{rhohprime equation}

@@

(\ref{rhohprime equation}) as the forcing.

@@

\underbrace{- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\eb_r\right] + \psi}_{\text{this term used to come in through} ~ (\rho h)_0^{n+1} - (\rho h)_0^n} + \wt\frac{\partial p_0}{\partial r} \enskip .

@@

+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + \wt\frac{\partial p_0}{\partial r} + \psi  \enskip .

@@

>>>>

\def\eb    {{\bf e}}
\def\Ub    {{\bf U}}
\def\Ubt   {\widetilde{\bf U}}
\def\ut    {\widetilde{\bf U}}
\def\wt    {\widetilde{w}}
\def\er    {{\bf e}_r}
\def\kth   {k_\mathrm{th}}

@@

+ \nabla\cdot \kth \nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\

@@

+ \underbrace{\psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kth\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.

@@

+ (\ut \cdot \er )\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 

@@

+ \psi + (\ut \dot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}

@@

- \nabla\cdot[(\rho h)_0\Ubt] + (\ut \cdot \er)\frac{\partial p_0}{\partial r} 
+ \nabla\cdot\kth\nabla T\nonumber \\

@@

- \nabla\cdot[(\rho h)_0\Ubt] + (\ut \cdot \er)\frac{\partial p_0}{\partial r}
+ \nabla\cdot\kth\nabla T}_{"(\rho h)' ~ \text{force}"}. \label{rhohprime equation}

@@

(\ref{rhohprime equation}) as the forcing. \MarginPar{{\tt full\_rhoh0\_evolution} comes into play here}

@@

\underbrace{- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\eb_r\right] + \psi}_{\text{this term used to come in through} ~ (\rho h)_0^{n+1} - (\rho h)_0^n} + (\ut \cdot \er)\frac{\partial p_0}{\partial r} \enskip .

@@

+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + (\ut \cdot \er)\frac{\partial p_0}{\partial r} + \psi  \enskip .

@@

\subsection{Predicting $h$ ({\tt enthalpy\_pred\_type = 2})}

\subsection{Predicting $T$ then $(\rho h)'$ ({\tt enthalpy\_pred\_type = 3})}

\subsection{Predicting $T$ then $h$ ({\tt enthalpy\_pred\_type = 4})}

\subsection{Summary of Forcing}

\begin{table*}[h]
\begin{center}
\caption{Forcing term into {\tt make\_edge\_scal} \newline}
\begin{tabular}{c|c}
\hline
\hline
{H PRED TYPE} &   {Force} \\
\hline \\[-3mm]
1  $((\rho h)^\prime)$ &  $(\ut \cdot \er) \frac{\partial p_0}{\partial r} - 
 (\rho h)^\prime \; \nabla \cdot (\ut+w_0 \er) - 
 \nabla \cdot (\ut (\rho h)_0) + \nabla \cdot \kth \nabla T$ \\[2 mm]
2  $(h)$ & $\frac{1}{\rho} \left [\psi + (\ut \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\[2 mm]
3  $(T)$ & $\frac{1}{\rho c_p} \left \{ (1 - \rho h_p) 
   \left [\psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} \right ] \nabla \cdot \kth \nabla T \right \}$ \\[2 mm]
4  $(T)$ & $\frac{1}{\rho c_p} \left\{ (1 - \rho h_p) \left [\psi + (\ut \cdot \er)
\frac{\partial p_0}{\partial r}\right ] \nabla \cdot \kth \nabla T \right\}$ \\[2 mm]
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}[h]
\begin{center}
\caption{Quantity that goes into and out of {\tt make\_edge\_scal} \newline}
\begin{tabular}{c|c}
\hline
\hline
{h pred type} & {h/T } \\
\hline \\[-3mm]
1 & $(\rho h)^\prime$ \\
2 & $h$  \\
3 & $T$  \\
4 & $T$  \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
\caption{When predicting temp ... (conversion done by {\tt makeRhoHfromT}) \newline}
\begin{tabular}{c|c|c|c}
\hline
\hline
{type} & {Inputs } & {EOS inputs} & {output} \\
\hline
3 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ &  $(\rho h)^\prime = \rho h - (\rho h)_0$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
 4 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ & $h$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
\caption{Quantity that goes into {\tt mkflux} on edges \newline}
\begin{tabular}{c|c|c}
\hline
\hline
{h pred type} & {Species } & {h/T } \\
\hline
1 & $X$ and $\rho^\prime$ & $(\rho h)^\prime$ \\
2 & $X$ and $\rho^\prime$ & $h$ \\
3 & $X$ and $\rho^\prime$ & $(\rho h)^\prime$ \\
4 & $X$ and $\rho^\prime$ & $h$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
\caption{Quantity that is created in mkflux and passed into update scal\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\ut+w_0)(\rho_0+\rho^\prime) X          $ & $(\ut+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\ut \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}
